---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# neocache

<!-- badges: start -->
[![R-CMD-check](https://github.com/alexpghayes/neocache/workflows/R-CMD-check/badge.svg)](https://github.com/alexpghayes/neocache/actions)
[![Codecov test coverage](https://codecov.io/gh/alexpghayes/neocache/branch/main/graph/badge.svg)](https://codecov.io/gh/alexpghayes/neocache?branch=main)
<!-- badges: end -->

`neocache` facilitates robust sampling of the Twitter graph. The basic idea is to save any data into a local cache as you as you get it. `neocache` is build on top of [`rtweet`](https://rtweet.info/), Docker, and Neo4J.

## Installation

You can install the development version of `neocache` with:

``` r
install.packages("devtools")
devtools::install_github("alexpghayes/neocache")
```

```{r}
library(neocache)

nc_sitrep()
```

### Find the personalized pagerank of a Twitter user and cache the following network in the process

**NOTE**: As of January 2022, the following does not work due to a change in the `rtweet` dev version that we have not yet updated `neocache` to accommodate.

```{r neocache-example, eval = FALSE}
alexpghayes_ppr <- appr(
  neocache_graph(),
  "alexpghayes",
  epsilon = 1e-4
)

alexpghayes_ppr$stats
```
